\section{Introduction}

%% DC 10: After seeing this I'm less convinced it was a good idea for me to suggest it, at least as an introduction.  It might read/work better as a related work section now, assuming that we have the previous work available to cite.  
In previous work, researchers have studied the relationship of different cohorts adopting new technologies and how users that did not grow in a technological environment show different characteristics when compared with the younger generations. This external variable to the social network might explain many different aspects of how adoption of a network happens. Just as users experience outside the network vary according to their age and influence their behavior, users' experience inside the network throughout time vary as the network evolves. Users in the early stages of a social network have a very different experience from latter users.

\textbf{\textit{Are users evolving in different ways based on when they join the network? How is an early user different from a late user?}}

Evolution in this sense can be interpreted in many different ways. Researchers have looked into many aspects of how user behavior change, how frequent they post, how users adopt new language, how likely a user is to survive in the network (which is also related with the problem of predicting which users are going to depart from your network). Based on this, we have to understand what we are looking for in the user behavior.

%% DC 10: This really isn't a separate question; these are common kinds of questions that realted work might ask
\textbf{\textit{What can ``different'' be? Effort, activity, survival?}}

This evolving process of users changing inside of the network change the network itself. We know that the idea users have from a social network might change their willingness to try it, just as we know how the initial experience might impact in the user future behavior \cite{Miller2015}. But the community evolving in itself changes the idea users outside have about it \cite{Danescu-niculescu-mizil2013}. This internal evolution together with the novelty that the influx of users bring make reddit a very interesting evironment to understand, for sub-communities known as subreddits as being created all the time and in different contexts, which raises the following question.

\textbf{\textit{Are communities evolving in different ways based on when they are created in the network?}}

%% DC 10: Problem. https://www.reddit.com/wiki/reddit_101 new users are subscribed by default to a number of subreddits, which I'm guessing explains an enormous amount of the advantage of reddits from 2008.  That makes this part much less interesting for us to talk about.  See if these subreddits were created mostly in 2008. http://i.imgur.com/4PxSX4e.png (and also, how this list has changed over time).
%%
%% DC 10: There's a reasonable chance there's still a fun paper just about users, but what we don't want to do is say that our cohort analysis really bought us something that would have been better bought by actually looking at site norms.

%% We can check weather the introduction or removal of subreddits in the default set influences significantly activity in them. Since the default are chosen based on the activity on them to begin with, it is more a positive reinforcement than a decisive bias for the community (as we can see, subreddits that are not ``doing well'' are removed, there is more on the comments in https://www.reddit.com/r/defaults). Even though, it might be worth to remove the subreddit section. We could also anlize wheather or not being included or removed from the default changes something for the community.
\begin{table}[htbp]
\centering
\tabcolsep=0.11cm
\singlespacing
\fontsize{7pt}{8pt}\selectfont
\begin{tabular}{|>{\raggedright\centering\arraybackslash}m{1.5cm}|m{6.8cm}|}
\hline
December 31, 2009 & announcements, AskReddit, blog, funny, gaming, pics, politics, programming, reddit.com, science, worldnews, WTF \\ \hline
October 18, 2011 & AdviceAnimals, Announcements, AskReddit, AskScience, Atheism, Aww, BestOf, Blog, Funny, Gaming, IamA, Movies, Music, Pics, Politics, Science, Technology, TodayILearned, Videos, WorldNews, WTF \\ \hline
October 19, 2012 & AdviceAnimals, Announcements, AskReddit, Aww, BestOf, Blog, Funny, Gaming, IamA, Movies, Music, News, Pics, Science, Technology, TodayILearned, Videos, WorldNews, WTF, Gifs, Television, Explainlikeimfive, Earthporn, books, AskScience \\ \hline
July 17, 2013 & AdviceAnimals, AskReddit, Aww, BestOf, Books, EarthPorn, ExplainLikeImFive, Funny, Gaming, Gifs, IAmA, Movies, Music, News, Pics, Science, Technology, Television, TodayILearned, Videos, WorldNews, WTF \\ \hline
January 1, 2014 & AdviceAnimals, AskReddit, AskScience, Aww, BestOf, Books, EarthPorn, ExplainLikeImFive, Funny, Futurology, Gaming, Gifs, IAmA, Movies, Music, News, Pics, Science, Sports, Technology, Television, TodayILearned, Videos, WorldNews \\ \hline
April 19, 2014 & AdviceAnimals, AskReddit, AskScience, Aww, BestOf, Books, EarthPorn, ExplainLikeImFive, Funny, Gaming, Gifs, IAmA, Movies, Music, News, Pics, Science, Sports, Television, TodayILearned, Videos, WorldNews \\ \hline
May 7, 2014 & announcements, Art, AskReddit, askscience, aww, blog, books, creepy, dataisbeautiful, DIY, Documentaries, EarthPorn, explainlikeimfive, Fitness, food, funny, Futurology, gadgets, gaming, GetMotivated, gifs, history, IAmA, InternetIsBeautiful, Jokes, LifeProTips, listentothis, mildlyinteresting, movies, Music, news, nosleep, nottheonion, oldschoolcool, personalfinance, philosophy, photoshopbattles, pics, science, Showerthoughts, space, sports, television, tifu, todayilearned, TwoXChromosomes, UpliftingNews, videos, worldnews, writingprompts \\ \hline
\end{tabular}
\caption{Default subrredits over time.}
\end{table}

\begin{table}[htbp]
\centering
\tabcolsep=0.11cm
\singlespacing
\fontsize{7pt}{8pt}\selectfont
\begin{tabular}{|>{\raggedright\centering\arraybackslash}m{1.5cm}|c|c|c|c|c|c|c|c|}
\hline
 & 2007 & 2008 & 2009 & 2010 & 2011 & 2012 & 2013 & 2014 \\ \hline
December 31, 2009 & 5 & 6 & 1 & - & - & - & - & - \\ \hline
October 18, 2011 & 3 & 14 & 2 & 2 & - & - & - & - \\ \hline
October 19, 2012 & 2 & 16 & 3 & 2 & 2 & - & - & - \\ \hline
July 17, 2013 & 2 & 15 & 2 & 1 & 2 & - & - & - \\ \hline
January 1, 2014 & 3 & 14 & 2 & 2 & 3 & - & - & - \\ \hline
April 19, 2014 & 3 & 13 & 2 & 2 & 2 & - & - & - \\ \hline
May 7, 2014 & 4 & 23 & 6 & 5 & 4 & 7 & 1 & - \\ \hline
\end{tabular}
\caption{Count of subreddits per creation year for each default set of.}
\end{table}

Kooti et al. \cite{Kooti2010} showed that social conventions can define the evolution of a community and the early adopters play a major role in designing these conventions, even if at the time this is not known by them. Evidence for the need of a retweeting mechanism in Twitter was evident in the early stages of the community and, out of the many possibilities that coexisted, the ``RT'' tag survived. Early adopters of these conventions are core users, well connected and presenting high activity. Just as Twitter, reddit network evolved from a relatively small set of users and subreddits. Wheather or not these early adopter of reddit laid the foundations in terms of content and behavior is not necessarily clear. It is reasonable to imagine that users would always look for content in subreddits that were created around the time they joined the network, for they might refer to the current context they are inserted into. Therefore, we propose the following question.

\textbf{\textit{Is there a consolidation point in a social network where the ``core content'' is established? Can this core change over time?}}

User-Network homophily? They connect because they are similar or do they become similar as the user evolves? Are the ``dissimilar'' leaving?
Looking at how reddit looked like at a particular point in time is a different question from how users evolve, and much of the user evolution depends on the environment a user finds when they first join the network. In many ways, this is an initial value problem, but separating what is due to the evolution of the network and what comes from the different demographics outside the network is not always clear.

\textbf{\textit{Are latter users intrinsically different from earlier users or are they having different initial experiences?}}
