\section{Time matters} 

\subsection{Why accounting for time is important}

Communities grow and, with time, die. For any community, its users play a role in its evolution, but they are also simultaneously affected by the evolution of the community. Untangling this interplay can help make sense of patterns of activity in a community.

One useful way to understand the evolution of a community and its users is through time, as it provides a linear account of the growth (or decay) of overall activity, types of content, and social norms and structure.  One aspect of time often considered is the tenure of a user in the community, as in studies around modeling users' preferences \cite{McAuley2013} or analyzing the evolution of their language \cite{Danescu-niculescu-mizil2013}.  These analyses uncover insights about the lifecycle of a user in a community: users' preferences and behavior change with their age in a community \cite{Panciera2010}, while their early experiences and activity shape future outcomes predictably \cite{Tan2015,Yang2009,Panciera2009, Miller2015}. 

However, much past work on online communities ignores the time at which a user joins the community and analyzes all users together.
%This line is redundant 
%, irrespective of when they joined a community. 
This might be a mistake: communities may grow denser or sparser with time \cite{Leskovec2005}, develop new norms \cite{Kooti2010}, and enact policies and rules guiding people's behavior \cite{Butler2008}.
These changes mean that people experience different versions of a community at different times, which can, in turn, affect their observed behavior. This interaction with the state of a community can confound conclusions about people's behavior, because the differences one observes may simply due to changes in the community, rather than any significant change in the outcome variable of interest or the user population.  


\subsection{Cohorts are analytically useful}

A common method to control for such confounds is cohort analysis, widely used in fields such as sociology \cite{Mason2012,Glenn2005}, economics \cite{Attanasio1993,Beldona2005}, and medicine \cite{Howartz1996,Davis2010}. A cohort is defined as a group of people who share a common characteristic, generally with respect to time. For example, people born in the same year, or those who joined a school at the same time, or got exposed to an intervention at similar times can be considered as cohorts.  People in a cohort are assumed to be exposed to the same state of the world and thus are more comparable to each other than to people in other cohorts. 

For example, sociological studies often use students who join a school in the same year to understand the effect of interventions \cite{Goyette2008,Alexander2012}, and condition on the year in which people were born to understand people's  behavior, such as variations in financial decision-making \cite{Attanasio1993} or opinions on issues \cite{Firebaugh1988,Jennings1996}. Similarly, medical studies interpret effects of drugs using cohorts of people within the same age group or amount of exposure to correlated conditions \cite{Howartz1996,Davis2010}.  

Recent work shows that cohorts' importance transfers to online communities as well. Just as people's behavior varies according to their biological age, their experience in an online community may vary with their age in the community and their year of joining. In Wikipedia, we find substantial differences in the activities of cohorts of users who joined earlier versus those who joined later \cite{Welser2011}. Similarly, on review websites, users who join later tend to adopt different phrases than the older users who had joined earlier \cite{Danescu-niculescu-mizil2013}.

\subsection{What might cause these differences?}

These differences in activity between cohorts may be due to a number of reasons.  One plausible explanation is selection effects: people who are enthusiastic about a community or its goals are more likely to self-select as early members of a community, while others may be more likely to join later \cite{Li2008}.  In this case, users who join earlier might be expected to be more active, committed users than those who join later. 

Another possible explanation is that community norms may change over time.  In many cases, it is a bottom-up process. Kooti et al. showed that social conventions can define the evolution of a community and the early adopters play a major role in designing these conventions, consciously or not \cite{Kooti2010}. Examples include adoption of `RT', a retweeting norm by Twitter users and the subsequent introduction of the Retweet button on Twitter \cite{Kooti2010}; change in language use between new and old users on review websites \cite{Danescu-niculescu-mizil2013}; and assumptions of clear roles and responsibilities on Wikipedia \cite{Kittur2007a}. In other cases, it may be directed by the community managers. For instance, the makers of Digg unilaterally changed the nature of the community by introducing a new version of the website, leading to a sudden change in norms and behavior in the community \cite{Ingram2014,Lardinois2014}. 

The growth of a community may also affect people's behavior. Successful communities often grow very rapidly, which can be both good and bad for users' experience. On one hand, growth would imply availability of a larger chunk of content to choose from. On the other, it might be harder to connect to others and get responses in a bigger community. A community may also need to adopt new rules and policies to manage growth and newcomers, as in the evolution of Wikipedia \cite{Choi2010,Bryant2005}. In those cases, the experience of later cohorts of users may be vastly different from the initial ones who joined before formal rules were in place. 

Finally, patterns of use may change because the overall population of Internet users is still changing.  As more and different people come online, their influx may lead to changes in activity patterns and communities (as with the yearly entry of college freshmen, and eventually all of AOL, gaining access to Usenet).  The gradual penetration of technology also has age-related effects:  people who did not grow up in a technological environment differ in their social media and search usage compared to younger generations\cite{Correa2010,Beldona2005}. 

%% Sam 8: Reworked this paragraph, added what was our initial research question and some cues on what we are going to see later on
% DC 14: Taking another shot at restatement that lays out what I think was closer to the original question.  Don't need to restate that the cohort findings are different here; we have that in the intro, and will show it soon enough. 

\subsection{Is Reddit getting ``worse'' over time?}
All of the above reasons suggest that users from different cohorts are likely to be different, which has also been demonstrated in online and offline communities \cite{Ryder1965,Danescu-niculescu-mizil2013,Prensky2001,Correa2010}.  Further, they suggest a general hypothesis that communities ``get worse'' over time because newer users are likely to be less committed and knowledgeable about the community. 

To address this hypothesis, we analyze both aggregate and cohort-based measures of user quality that are often raised about online communities: how active are users \cite{Scellato2011,Hughes2009,Java2007,Levy1984}, how much do they contribute \cite{Scellato2011,Gruhl2004,Guo2009}, and what kinds of work do they engage in \cite{Welser2011,Choi2010,Panciera2009}?  

We do this in the context of Reddit, a community that has been studied by many researchers \cite{Gilbert2013,Stoddard2015,Bergstrom2011,Tan2015}. We begin with a brief overview of both Reddit and the dataset that we use in this paper, focusing on aspects that directly impact our analyses\footnote{There is more to say about Reddit itself (see \cite{AboutReddit}).}.

% All of the above reasons suggest that users from different cohorts are likely to be different, which has also been demonstrated in online and offline communities \cite{Ryder1965,Danescu-niculescu-mizil2013,Prensky2001,Correa2010}. In this paper, our motivating research question was ``How users' behavior evolve when accounting for cohorts?''. To do so, we considered as behavior their activity levels, effort when commenting and kinds of contributions in the network. As we will see, users from different cohorts exhibit significant differences in behavior. More than that, we find that not accounting for underlying time-evolving processes of the network might lead to wrong conclusions about their behavior.
%% Sam 8: Removing this, too vague
%Accounting for these differences can be helpful for making conclusions about outcomes of interest, such as user's activity levels, their survival, among many other possibilities.